Ricci-Ollivier Curvature of two Random Walks on the Rooted Phylogenetic Subtree-prune-regraft Graph

### 2015-03-20 curvature.tex
IEEEtran style. Shifted margins left to allow for notes on the right side

\documentclass{amsart}

\usepackage{amsmath,amsthm}
\usepackage[foot]{amsaddr}
\usepackage{ifthen}
\usepackage{todonotes}
\usepackage[notref,notcite]{showkeys} % show keys for eqs, etc.
\usepackage{cite}
\usepackage{enumitem}
\usepackage{url}
%\usepackage[margin=1in]{geometry}

@@

\begin{document}
\title[Curvature of phylogenetic subtree-prune-regraft graph]{Ricci-Ollivier curvature of two random walks on rooted phylogenetic subtree-prune-regraft graph}
\author[Whidden and Matsen]{Christopher Whidden$^1$ and Frederick A Matsen IV$^1$}
\address{$^1$Program in Computational Biology, Fred Hutchinson Cancer Research Center, Seattle, WA, 98199}
\email{cwhidden@fredhutch.org}
\email{matsen@fredhutch.org}
\thanks{}

\date{\today}

@@

\maketitle
\pagebreak

>>>>

\documentclass[11pt,onecolumn,conference]{IEEEtran}

\usepackage{amsmath,amsthm}
\usepackage{ifthen}
\usepackage{todonotes}
%\usepackage[notref,notcite]{showkeys} % show keys for eqs, etc.
\usepackage[right]{showlabels}
\usepackage{cite}
\usepackage{enumitem}
\usepackage{url}
% shift for todonotes
\usepackage[left=0.5in,right=1.5in,top=1in,bottom=1in,marginparwidth=1.25in]{geometry}
% regular margins
%\usepackage[margin=1in]{geometry}

@@

\begin{document}
\title{Ricci-Ollivier Curvature of two Random Walks on the Rooted Phylogenetic Subtree-prune-regraft Graph}

\author{
	\IEEEauthorblockN{Christopher Whidden}
	\IEEEauthorblockA{Program in Computational Biology\\
	Fred Hutchinson Cancer Research Center\\
	Seattle, WA 98199\\
	Email: cwhidden@fredhutch.org}
	\and
	\IEEEauthorblockN{Frederick A Matsen IV}
	\IEEEauthorblockA{Program in Computational Biology\\
	Fred Hutchinson Cancer Research Center\\
	Seattle, WA 98199\\
	Email: matsen@fredhutch.org}
}

\maketitle
\IEEEpeerreviewmaketitle

@@
